Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs

### 2020-08-10 FDT2020/main-section.tex
linking lambda and gamma

\begin{proof}	
	Consider the following linear program which we denote by $\LPC(\ell,x')$. The variables of $\LPC(\ell,x')$ are $\gamma_0,\gamma_1$ and $x^0$ and $x^1$.
\cindy{I think you mean that the $\lambda$s are variables, not $\gamma$s.  However the above lemma uses $\gamma$ and then there is a mix of $\lambda$ and $\gamma$ below the LP. Can you please check that you intend to have both types and they are used properly?}
	\begin{align}
	\LPC(\ell,x')\quad\quad& \max\quad \;\lambda_0+\lambda_1\\
	&\;\text{s.t.} \quad Ax^j \geq b\lambda_j & \mbox{ for $j=0,1$} \label{feasibility}\\
	&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq \lambda_j &\mbox{ for $j=0,1$}\label{bound}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^0_\ell = 0,\; x^1_\ell =\lambda_1\label{branchcoordinate}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1 \leq x'\label{packing}\\
	&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1 \geq 0
	\end{align}

	Let $x^0,x^1$, and $\gamma_0,\gamma_1$ be an optimal solution to the LP above. Let $\hat{x}^0 = x^0/\gamma_0$, $\hat{x}^1=x^1/\gamma_1$. This choice satisfies  (ii), (iii), (iv). To show that (i) is also satisfied we prove the following claim.

@@

\begin{lemma}\label{prune}
	There is a polynomial time algorithm that produces sets $L_0,\ldots,L_t$ of pairs of $x\in \dom(P)$ together with multipliers $\lambda$ with the following properties for $i=0,\ldots,t$:
	(a) If $x\in L_i$, then $x_j \in \{0,1\}$ for $j\in [i]$, i.e. the first $i$ coordinates of a solution in level $i$ are integral, (b) $\sum_{[x,\lambda]\in L_i} \lambda\geq\frac{1}{g^i}$, (c) $\sum_{[x,\lambda]\in L_i}\lambda x \leq x^*$, (d) $|L_i|\leq t$.
\end{lemma}
\begin{proof}
	We prove this lemma using induction but one can clearly see how to turn this proof into a polynomial time algorithm. Let $L_0$ be the set that contains a single node (\textit{root of the FDT tree}) with $x^*$ and multiplier 1. It is easy to check all the requirements in the lemma are satisfied for this choice.

>>>>

\begin{proof}	
	Consider the following linear program which we denote by $\LPC(\ell,x')$. The variables of $\LPC(\ell,x')$ are $\lambda_0$, $\lambda_1$, $x^0$ and $x^1$.
% \cindy{I think you mean that the $\lambda$s are variables, not $\gamma$s.  However the above lemma uses $\gamma$ and then there is a mix of $\lambda$ and $\gamma$ below the LP. Can you please check that you intend to have both types and they are used properly?}
	\begin{align}
	\LPC(\ell,x')\quad\quad& \max\quad \;\lambda_0+\lambda_1\\
	&\;\text{s.t.} \quad Ax^j \geq b\lambda_j & \mbox{ for $j=0,1$} \label{feasibility}\\
	&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq \lambda_j &\mbox{ for $j=0,1$}\label{bound}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^0_\ell = 0,\; x^1_\ell =\lambda_1\label{branchcoordinate}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1 \leq x'\label{packing}\\
	&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1 \geq 0
	\end{align}

	Let $x^0$, $x^1$, $\lambda_0$, and $\lambda_1$ be an optimal solution to the LP above. Set $\gamma_0=\lambda_0$ and $\gamma_1 = lambda_1$.
\cindy{The sentence right before this is how I think you link the $\lambda$ in the LP to the $\gamma$ constants in the Lemma statement and the claim below, etc.}
Let $\hat{x}^0 = x^0/\gamma_0$, $\hat{x}^1=x^1/\gamma_1$. This choice satisfies  (ii), (iii), (iv). To show that (i) is also satisfied we prove the following claim.

@@

\begin{lemma}\label{prune}
	There is a polynomial time algorithm that produces sets $L_0,\ldots,L_t$ of pairs of $x\in \dom(P)$ together with multipliers $\lambda$ with the following properties for $i=0,\ldots,t$:
	(a) If $x\in L_i$, then $x_j \in \{0,1\}$ for $j\in [i]$, i.e. the first $i$ coordinates of a solution in level $i$ are integral, (b) $\sum_{[x,\lambda]\in L_i} \lambda\geq\frac{1}{g^i}$, (c) $\sum_{[x,\lambda]\in L_i}\lambda x \leq x^*$, (d) $|L_i|\leq t$.
\end{lemma}
\begin{proof}
	We prove this lemma using induction but one can clearly see how to turn this proof into a polynomial time algorithm. Let $L_0$ be the set that contains a single node (\textit{root of the FDT tree}) with $x^*$ and multiplier 1. All the requirements in the lemma are satisfied for this choice.
